---
title: "R Notebook"
output: html_notebook
author: Ben Maylor
---

# Batch Calculate Cadence Metrics

Last updated: `20/12/2025`

**Purpose:** Generate cadence metrics (peak 1-min and peak 30-min cadence) using 60s epoch data generated by either PALbatch or Actilife.

**Output:** Exports an `softwareinfo_Daily_Cadence.csv` file with the cadence metrics calculated at the day level for merging with other phenotypes prior to downstream analysis.

## Setup

Load libraries and specify data folder in here.

```{r setup}
pacman::p_load(dplyr, data.table)
files <- list.files(path = "path/to/dir", pattern = ".csv", full.names = T)
```

## Process

When running this chunk you will be prompted to select either `PB` or `AL` based on where the 60s epoch data is derived from. The rest is taken care of.

```{r process}

answer <- readline(prompt = "Is the minute-level data from the palbatch (pb) or actilife (al): ")

if(tolower(answer) == "pb") {
  message("processing palbatch data!")
  
  master_df <- data.frame(
    Filename = character(0),
    ID = character(0),
    SerialNumber = character(0),
    Date = as.Date(character(0)),
    daily_steps = integer(0),
    peak_1_cadence = numeric(0),
    peak_30_cadence = numeric(0)
  )
  
    for (i in 1:length(files)){
      # File info
      filename <- basename(files[i])
      pid <- substr(filename, 1, 7) # for SWL data based on a 7-digit ID
      serial_number <- substr(filename, 9, 16) # As an additional measure to assist with merging in case of duplicate ID's
        
      # Read data
      df <- fread(files[i], data.table = F)
      
      # Generate cadence metrics
      df <- df %>%
        mutate(Date = as.Date(`Time(approx)`)) %>%
        group_by(Date) %>%
        summarise(
          daily_steps = sum(StepCount, na.rm = TRUE),
          peak_1_cadence = max(StepCount, na.rm = TRUE),
          peak_30_cadence = mean(head(sort(StepCount, decreasing = TRUE), 30), na.rm = TRUE),
          .groups = "drop"
          ) %>%
        mutate(Filename = filename, ID = pid, SerialNumber = serial_number)
      
      # Re-order cols   
      df <- df %>%
        select(
          Filename,
          ID,
          SerialNumber,
          Date,
          daily_steps,
          peak_1_cadence,
          peak_30_cadence
        )
      
      # Add to master output file
      master_df <- rbind(master_df, df)
      
      # Update user on progress throughout
      cat("\rFile", i, "of", length(files), "Processed")
      
    } # End loop
  palbatch_info <- sub(".*-([A-Z]+-[^-]+-Epochs1m)\\.csv", "\\1", files[1])
  fwrite(master_df, file = paste0(palbatch_info, "_Daily_Cadence.csv"))
  print("Finished!")
  
  
} else if (tolower(answer) == "al") { 
    message("processing actilife data!")
  
  master_df <- data.frame(
    Filename = character(0),
    ID = character(0),
    SerialNumber = character(0),
    Date = as.Date(character(0)),
    daily_steps = integer(0),
    peak_1_cadence = numeric(0),
    peak_30_cadence = numeric(0)
  )
  
  for (i in 1:length(files)) {
    
    # File info
    filename <- basename(files[i])
    pid <- sub("_.*", "", filename)
  
    # Read data
    df <- fread(files[i])
    
    # Generate cadence metrics
    df <- df %>%
      mutate(Date = as.Date(timestamp)) %>%
      group_by(Date) %>%
      summarise(
        daily_steps = sum(steps, na.rm = TRUE),
        peak_1_cadence = max(steps, na.rm = TRUE),
        peak_30_cadence = mean(head(sort(steps, decreasing = TRUE), 30), na.rm = TRUE),
        .groups = "drop"
      ) %>%
      mutate(Filename = filename, ID = pid)
    
      # Re-order cols   
      df <- df %>%
        select(
          Filename,
          ID,
          Date,
          daily_steps,
          peak_1_cadence,
          peak_30_cadence
        )
    # Add to master output file
    master_df <- rbind(master_df, df)
    
    # Update user on progress throughout
    cat("\rFile", i, "of", length(files), "Processed")
    
  } # End loop
  
  fwrite(master_df, file = "Actilife_Daily_Cadence.csv")
  print("Finished!")
  
} else { 
    message("You must choose 'PB' or 'AL' options! Try again")
  }

```

END
