---
title: "05_external_validation"
output: html_document
author: Charilaos Zisou
---

# Analysis

## Setup

```{r}
rm(list=ls())

# Load required packages
if (!require(pacman)) install.packages("pacman")
pacman::p_load(here, data.table, dplyr, tidyr, gtsummary, grid, gridExtra, gt, ckbplotr, purrr)

# Load helper functions
source(here("R", "2-analysis", "utils_analysis.R"))
source(here("R", "2-analysis", "utils_display.R"))

# Initialise filenames
comparability_qced_D_phenotypes_filename <- "comparability_qced_D_phenotypes.csv"
comparability_qced_ND_phenotypes_filename <- "comparability_qced_ND_phenotypes.csv"
comparability_demographics_filename <- "comparability_demographics_cleaned.csv"
```

## Load data

```{r}
# Load physical activity data
dat_D_qced <- data.table::fread(
  here("output", "comparability", comparability_qced_D_phenotypes_filename),
  data.table = FALSE
)

dat_ND_qced <- data.table::fread(
  here("output", "comparability", comparability_qced_ND_phenotypes_filename),
  data.table = FALSE
)

# Load demographics data
comparability_demographics <- data.table::fread(
  here("output", "comparability", comparability_demographics_filename),
  data.table = FALSE
)

# Convert MVPA from hours to mins
dat_D_qced <- dat_D_qced %>%
  mutate(across(starts_with("mvpa"), ~ .x * 60))

dat_ND_qced <- dat_ND_qced %>%
  mutate(across(starts_with("mvpa"), ~ .x * 60))

# Convert wear time from total hours to daily hours
dat_D_qced   <- add_daily_wear(dat_D_qced)
dat_ND_qced <- add_daily_wear(dat_ND_qced)
```



## Table S4: Participant characteristics

```{r}
# Keep only participants that pass QC
comparability_demographics <- comparability_demographics %>%
  filter(pid %in% dat_ND_qced$pid)

# Prepare new categories
comparability_demographics <- comparability_demographics %>%
  mutate(
    sex = case_when(
      sex == "M" ~ "Male",
      sex == "F" ~ "Female",
      TRUE ~ NA_character_
    ),
    education_cat = case_when(
      education %in% c("A-Levels", "College", "Diploma", "MVQ Level 4") ~ "Further education",
      education %in% c("Undergraduate", "Postgraduate", "BMBCH") ~ "University degree",
      TRUE ~ NA_character_
    ),
    employment_cat = case_when(
      employment %in% c("Full-time", "Part-time") ~ "Employed",
      employment %in% c("Student", "Part-time-student") ~ "Student",
      TRUE ~ NA_character_
    ), 
    bmi_3gp = cut(
      comparability_demographics$bmi,
      breaks = c(-Inf, 25, 30, Inf),
      labels = c("<24.9", "25-29.9", "30+"),
      right = FALSE
    )
  )

# Prepare relevant columns
comparability_demographics <- comparability_demographics %>%
  select(age,
         sex,
         employment_cat,
         education_cat,
         bmi_3gp) %>%
  mutate(sex = factor(sex, levels = c("Male", "Female")),
         employment_cat = factor(employment_cat,
                                 levels = c("Not employed", "Student", "Employed")),
         education_cat = factor(education_cat,
                                levels = c("No education",
                                           "Basic education",
                                           "Further education",
                                           "University degree")),
         bmi_3gp = factor(bmi_3gp, 
                          levels = c("<24.9", "25-29.9", "30+")))

# Convert NA to "Missing" category
comparability_demographics <- convert_na_to_missing(comparability_demographics,
                                                    c("sex",
                                                      "employment_cat",
                                                      "education_cat", 
                                                      "bmi_3gp"))

# Prep labels for Table 1
row_labels <- list(age = "Age (years)",
                   sex = "Sex",
                   employment_cat = "Employment status",
                   education_cat = "Education",
                   bmi = "Body mass index (kg/m2)")

# Build table 1 by study
table <- comparability_demographics %>%
  tbl_summary(label = row_labels,
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} ({p}%)"),
              digits = list(age ~ 1),
              missing = "no") %>%
  modify_spanning_header(all_stat_cols() ~ "**Study**") %>%
  remove_footnote_header() %>%
  bold_labels()

table

# Save Table S4 to .docx
table %>%
  as_gt() %>%
  gt::gtsave(here("output", "prepared", "tables", "Table_S4.docx"))
```

## Table S5: Descriptive statistics of accelerometer-derived phenotypes

```{r}
# Define phenotype columns/rows and labels
pa_rows <- c("overall_activity", 
             "steps", 
             "cadence_peak1",
             "mvpa", 
             "lipa", 
             "sedentary")

pa_labels <- list(overall_activity = "Overall activity (mg/day)",
                  steps            = "Step count (steps/day)",
                  cadence_peak1    = "Peak 1-min cadence (steps/minute)",
                  mvpa             = "MVPA (minutes/day)",
                  lipa             = "Light physical activity (hours/day)",
                  sedentary        = "Sedentary behaviour (hours/day)",
                  daily_wear_time_hours  = "Wear time (hours/day)")

cols <- c("Comparability_wrist", "Comparability_thigh", "Comparability_hip")

col_labels <- c(label = "**Phenotype**",
                Comparability_wrist = "**Comparability (wrist)**",
                Comparability_thigh = "**Comparability (thigh)**",
                Comparability_hip = "**Comparability (hip)**")

# Prep in wide format
comparability_wide   <- prep_wide(dat_ND_qced,  "Comparability")

comparability_wide <- comparability_wide %>%
  select(study_wear_location, all_of(c("daily_wear_time_hours", pa_rows))) %>%
  mutate(study_wear_location = factor(study_wear_location, levels = cols),
         across(all_of(c("daily_wear_time_hours", pa_rows)), as.numeric))

# Build summary table
table <- comparability_wide %>%
  tbl_summary(by = study_wear_location,
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               mvpa ~ "{median} ({p25}–{p75})",
                               daily_wear_time_hours ~ "{median} ({p25}–{p75})"),
              label = pa_labels,
              digits = list(all_continuous() ~ 1,
                            steps ~ 0,
                            mvpa ~ 0),
              missing = "no")

# Apply clean column labels in correct order
table <- table %>%
  modify_header(label ~ col_labels["label"],
                stat_1 ~ col_labels["Comparability_wrist"],
                stat_2 ~ col_labels["Comparability_thigh"],
                stat_3 ~ col_labels["Comparability_hip"]) %>%
  modify_footnote(everything() ~ NA) %>%
  bold_labels()

table

# Save Table S5 to .docx
table %>%
  as_gt() %>%
  gt::gtsave(here("output", "prepared", "tables", "Table_S5.docx"))
```

## Calibration of phenotypes using derived equations

```{r}
dat_thigh <- dat_ND_qced %>%
  select(-ends_with("hip"))

dat_hip <- dat_ND_qced %>%
  select(-ends_with("thigh"))

# Wrist vs Thigh
dat_thigh$overall_activity_mean_thigh = 3.05/0.884 + 1/0.884 * dat_thigh$overall_activity_mean_thigh
dat_thigh$steps_mean_thigh = 309/0.983 + 1/0.983 * dat_thigh$steps_mean_thigh
dat_thigh$cadence_peak1_mean_thigh = 17.6/1.16 + 1/1.16 * dat_thigh$cadence_peak1_mean_thigh
dat_thigh$mvpa_mean_thigh = pmax(0, -4.73/0.721 + 1/0.721 * dat_thigh$mvpa_mean_thigh)
dat_thigh$lipa_mean_thigh = -0.29/1.01 + 1/1.01 * dat_thigh$lipa_mean_thigh
dat_thigh$sedentary_mean_thigh = 0.091/0.928 + 1/0.928 * dat_thigh$sedentary_mean_thigh

# Wrist vs Hip
dat_hip$overall_activity_mean_hip = 3.51/0.803 + 1/0.803 * dat_hip$overall_activity_mean_hip
dat_hip$steps_mean_hip = 95.2/0.732 + 1/0.732 * dat_hip$steps_mean_hip
dat_hip$cadence_peak1_mean_hip = 73.7/1.61 + 1/1.61 * dat_hip$cadence_peak1_mean_hip
dat_hip$mvpa_mean_hip = pmax(0, -11.1/0.952 + 1/0.952 * dat_hip$mvpa_mean_hip)
dat_hip$lipa_mean_hip = -1.8/0.785 + 1/0.785 * dat_hip$lipa_mean_hip
dat_hip$sedentary_mean_hip = -1.04/0.824 + 1/0.824 * dat_hip$sedentary_mean_hip
```

## Figure 2: Absolute agreement ICCs

```{r}
thigh_icc_df <- map_dfr(pa_rows, function(pheno) {
  icc_swl <- calculate_icc(
    df   = dat_thigh,
    col1 = paste0(pheno, "_mean_wrist"),
    col2 = paste0(pheno, "_mean_thigh"),
    fmt_sep = ","
  )

  tibble(
    phenotype = pheno,
    est = icc_swl$icc_est,
    lci = icc_swl$icc_lci,
    uci = icc_swl$icc_uci
  )
})

hip_icc_df <- map_dfr(pa_rows, function(pheno) {
  icc_raine <- calculate_icc(
    df   = dat_hip,
    col1 = paste0(pheno, "_mean_wrist"),
    col2 = paste0(pheno, "_mean_hip"),
    fmt_sep = ","
  )

  tibble(
    phenotype = pheno,
    est = icc_raine$icc_est,
    lci = icc_raine$icc_lci,
    uci = icc_raine$icc_uci
  )
})

vlines <- list(
  ggplot2::geom_vline(xintercept = 0.75,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4)

)

forestplot_labels <- data.frame(
  phenotype = pa_rows,
  label = unname(unlist(pa_labels[pa_rows]))
)

figure <- ckbplotr::forest_plot(
  list ("CAP-24 study (wrist vs. thigh)" = thigh_icc_df, "CAP-24 study (wrist vs. hip)" = hip_icc_df),
  row.labels = forestplot_labels,
  col.key = "phenotype",
  col.estimate = "est",
  col.lci = "lci",
  col.uci = "uci",
  exponentiate = FALSE,
  xlim = c(0, 1),
  xticks = c(0, 0.25, 0.5, 0.75, 1),
  xlab = c("ICC"),
  right.heading = "ICC (95% CI)",
  panel.width = unit(50, "mm"),
  base_size = 10,
  add = list(start = vlines)
)

ggsave(
  filename = here("output", "prepared", "figures", "Figure_2.png"),
  plot = figure$plot,
  width = 23,
  height = 8,
  units = "cm",
  dpi = 300,
  bg = "white"
)
```

## Figure 3: Equivalence tests

```{r}
eq_zone <- 0.1

equi_test_thigh_list <- list()
equi_test_hip_list <- list()

for (pheno in pa_rows) {

  res_thigh <- equivalence_test(dat_thigh, paste0(pheno, "_mean"), eq_zone)
  res_hip <- equivalence_test(dat_hip, paste0(pheno, "_mean"), eq_zone)

  equi_test_thigh_list[[pheno]] <- data.frame(
    phenotype = pheno,
    mean_ratio = res_thigh$mean_ratio,
    lci = res_thigh$lci,
    uci = res_thigh$uci,
    is_equivalent = res_thigh$is_equivalent
  )

  equi_test_hip_list[[pheno]] <- data.frame(
    phenotype = pheno,
    mean_ratio = res_hip$mean_ratio,
    lci = res_hip$lci,
    uci = res_hip$uci,
    is_equivalent = res_hip$is_equivalent
  )
}

equi_test_thigh <- do.call(rbind, equi_test_thigh_list)
equi_test_hip <- do.call(rbind, equi_test_hip_list)

row.names(equi_test_thigh) <- NULL
row.names(equi_test_hip) <- NULL

vlines <- list(
  ggplot2::geom_vline(xintercept = 1 - eq_zone,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4),
  ggplot2::geom_vline(xintercept = 1 + eq_zone,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4)
)

forestplot_labels <- data.frame(
  phenotype = pa_rows,
  label = unname(unlist(pa_labels[pa_rows]))
)

figure <- ckbplotr::forest_plot(
  list ("CAP-24 study (wrist vs. thigh)" = equi_test_thigh, "CAP-24 study (wrist vs. hip)" = equi_test_hip),
  row.labels = forestplot_labels,
  col.key = "phenotype",
  col.estimate = "mean_ratio",
  col.lci = "lci",
  col.uci = "uci",
  exponentiate = FALSE,
  xlim = c(0.80, 1.20),
  xlab = c("Mean ratio (Thigh/Wrist)", "Mean ratio (Hip/Wrist)"),
  right.heading = "Mean ratio (90% CI)",
  nullval = TRUE,
  panel.width = unit(50, "mm"),
  base_size = 10,
  left.gap = c("I", "I"),
  add = list(start = vlines)
)

ggsave(
  filename = here("output", "prepared", "figures", "Figure_3.png"),
  plot = figure$plot,
  width = 23,
  height = 8,
  units = "cm",
  dpi = 300,
  bg = "white"
)
```

## Figure S11: Scatter plots

```{r}
# Initialise constants
inner_pad <- 0.02   # fraction of npc to expand box
gap       <- 0.04   # relative gap between panels A and B

# Prepare individual scatter plots for SWL
plot1 <- make_scatter_plot(dat_thigh,
                           phenotype = 'overall_activity_mean', 
                           title = 'Overall activity',
                           phenotype_units = 'mg/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 60))

plot2 <- make_scatter_plot(dat_thigh, 
                           phenotype = 'steps_mean', 
                           title = 'Step count',
                           phenotype_units = 'steps/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 30000))

plot3 <- make_scatter_plot(dat_thigh, 
                           phenotype = 'cadence_peak1_mean', 
                           title = 'Peak 1-min cadence',
                           phenotype_units = 'steps/minute',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(60, 180))

plot4 <- make_scatter_plot(dat_thigh, 
                           phenotype = 'mvpa_mean', 
                           title = 'MVPA',
                           phenotype_units = 'minutes/day',
                           skewed_phenotype = TRUE,
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 200))

plot5 <- make_scatter_plot(dat_thigh, 
                           phenotype = 'lipa_mean', 
                           title = 'Light physical activity',
                           phenotype_units = 'hours/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 12))

plot6 <- make_scatter_plot(dat_thigh, 
                           phenotype = 'sedentary_mean', 
                           title = 'Sedentary behaviour',
                           phenotype_units = 'hours/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(4, 16))

# Combine all SWL plots
panel_a <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)

# Prepare individual scatter plots for Raine
plot1 <- make_scatter_plot(dat_hip, 
                           phenotype = 'overall_activity_mean', 
                           title = 'Overall activity',
                           phenotype_units = 'mg/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 60))

plot2 <- make_scatter_plot(dat_hip, 
                           phenotype = 'steps_mean', 
                           title = 'Step count',
                           phenotype_units = 'steps/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 30000))

plot3 <- make_scatter_plot(dat_hip, 
                           phenotype = 'cadence_peak1_mean', 
                           title = 'Peak 1-min cadence',
                           phenotype_units = 'steps/minute',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(60, 180))

plot4 <- make_scatter_plot(dat_hip, 
                           phenotype = 'mvpa_mean', 
                           title = 'MVPA',
                           phenotype_units = 'minutes/day',
                           skewed_phenotype = TRUE,
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 200))

plot5 <- make_scatter_plot(dat_hip, 
                           phenotype = 'lipa_mean', 
                           title = 'Light physical activity',
                           phenotype_units = 'hours/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(0, 12))

plot6 <- make_scatter_plot(dat_hip, 
                           phenotype = 'sedentary_mean', 
                           title = 'Sedentary behaviour',
                           phenotype_units = 'hours/day',
                           show_equation = FALSE,
                           include_fit_line = FALSE,
                           axes_lims = c(4, 16))

# Combine all Raine plots
panel_b <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)

# Add titles to each panel
panel_a <- gridExtra::arrangeGrob(
  panel_a,
  top = grid::textGrob(
    "A. CAP-24 study (wrist vs. thigh)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

panel_b <- gridExtra::arrangeGrob(
  panel_b,
  top = grid::textGrob(
    "B. CAP-24 study (wrist vs. hip)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

# Add black borders around each panel
panel_a <- grid::grobTree(
  panel_a,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"), 
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

panel_b <- grid::grobTree(
  panel_b,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"),
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

# Stack the two boxed panels
figure <- gridExtra::arrangeGrob(panel_a,
                                 grid::nullGrob(),
                                 panel_b,
                                 ncol = 1,
                                 heights = c(1, gap, 1))

# Add small outer margin
figure <- ggplot() +
  theme_void() +
  annotation_custom(figure) +
  theme(plot.margin = grid::unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

# Save figure to file
ggsave(filename = here("output", "prepared", "figures", "Figure_S11.png"),
       plot = figure,
       width = 21,
       height = 29.7,
       units = "cm",
       dpi = 300,
       bg = "white")
```

## Figure S12: Bland-Altman plots

```{r}
# Initialise constants
inner_pad <- 0.02   # fraction of npc to expand box
gap       <- 0.04   # relative gap between panels A and B

# Prepare individual scatter plots for SWL
plot1 <- make_bland_altman_plot(dat_thigh, 
                                'overall_activity_mean', 
                                'Overall activity',
                                phenotype_units = 'mg/day')

plot2 <- make_bland_altman_plot(dat_thigh, 
                                'steps_mean', 
                                'Step count',
                                phenotype_units = 'steps/day',
                                digits = 0)

plot3 <- make_bland_altman_plot(dat_thigh, 
                                'cadence_peak1_mean', 
                                'Peak 1-min cadence',
                                phenotype_units = 'steps/minute')

plot4 <- make_bland_altman_plot(dat_thigh, 
                                'mvpa_mean', 
                                'MVPA',
                                phenotype_units = 'minutes/day')

plot5 <- make_bland_altman_plot(dat_thigh, 
                                'lipa_mean', 
                                'Light physical activity',
                                phenotype_units = 'hours/day')

plot6 <- make_bland_altman_plot(dat_thigh, 
                                'sedentary_mean', 
                                'Sedentary behaviour',
                                phenotype_units = 'hours/day')

# Combine all SWL plots
panel_a <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)

# Prepare individual scatter plots for Raine
plot1 <- make_bland_altman_plot(dat_hip, 
                                'overall_activity_mean', 
                                'Overall activity',
                                phenotype_units = 'mg/day')

plot2 <- make_bland_altman_plot(dat_hip, 
                                'steps_mean', 
                                'Step count',
                                phenotype_units = 'steps/day',
                                digits = 0)

plot3 <- make_bland_altman_plot(dat_hip, 
                                'cadence_peak1_mean', 
                                'Peak 1-min cadence',
                                phenotype_units = 'steps/minute')

plot4 <- make_bland_altman_plot(dat_hip, 
                                'mvpa_mean', 
                                'MVPA',
                                phenotype_units = 'minutes/day')

plot5 <- make_bland_altman_plot(dat_hip, 
                                'lipa_mean', 
                                'Light physical activity',
                                phenotype_units = 'hours/day')

plot6 <- make_bland_altman_plot(dat_hip, 
                                'sedentary_mean', 
                                'Sedentary behaviour',
                                phenotype_units = 'hours/day')

# Combine all Raine plots
panel_b <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)


# Add titles to each panel
panel_a <- gridExtra::arrangeGrob(
  panel_a,
  top = grid::textGrob(
    "A. CAP-24 study (wrist vs. thigh)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

panel_b <- gridExtra::arrangeGrob(
  panel_b,
  top = grid::textGrob(
    "B. CAP-24 study (wrist vs. hip)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

# Add black borders around each panel
panel_a <- grid::grobTree(
  panel_a,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"), 
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

panel_b <- grid::grobTree(
  panel_b,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"),
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

# Stack the two boxed panels
figure <- gridExtra::arrangeGrob(panel_a,
                                 grid::nullGrob(),
                                 panel_b,
                                 ncol = 1,
                                 heights = c(1, gap, 1))

# Add small outer margin
figure <- ggplot() +
  theme_void() +
  annotation_custom(figure) +
  theme(plot.margin = grid::unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

# Save figure to file
ggsave(filename = here("output", "prepared", "figures", "Figure_S12.png"),
       plot = figure,
       width = 21,
       height = 29.7,
       units = "cm",
       dpi = 300,
       bg = "white")
```

## Dominant wrist

```{r}
dat_thigh_D <- dat_D_qced %>%
  select(-ends_with("hip"))

dat_hip_D <- dat_D_qced %>%
  select(-ends_with("thigh"))

# Wrist vs Thigh
dat_thigh_D$overall_activity_mean_thigh = 3.05/0.884 + 1/0.884 * dat_thigh_D$overall_activity_mean_thigh
dat_thigh_D$steps_mean_thigh = 309/0.983 + 1/0.983 * dat_thigh_D$steps_mean_thigh
dat_thigh_D$cadence_peak1_mean_thigh = 17.6/1.16 + 1/1.16 * dat_thigh_D$cadence_peak1_mean_thigh
dat_thigh_D$mvpa_mean_thigh = pmax(0, -4.73/0.721 + 1/0.721 * dat_thigh_D$mvpa_mean_thigh)
dat_thigh_D$lipa_mean_thigh = -0.29/1.01 + 1/1.01 * dat_thigh_D$lipa_mean_thigh
dat_thigh_D$sedentary_mean_thigh = 0.091/0.928 + 1/0.928 * dat_thigh_D$sedentary_mean_thigh

# Wrist vs Hip
dat_hip_D$overall_activity_mean_hip = 3.51/0.803 + 1/0.803 * dat_hip_D$overall_activity_mean_hip
dat_hip_D$steps_mean_hip = 95.2/0.732 + 1/0.732 * dat_hip_D$steps_mean_hip
dat_hip_D$cadence_peak1_mean_hip = 73.7/1.61 + 1/1.61 * dat_hip_D$cadence_peak1_mean_hip
dat_hip_D$mvpa_mean_hip = pmax(0, -11.1/0.952 + 1/0.952 * dat_hip_D$mvpa_mean_hip)
dat_hip_D$lipa_mean_hip = -1.8/0.785 + 1/0.785 * dat_hip_D$lipa_mean_hip
dat_hip_D$sedentary_mean_hip = -1.04/0.824 + 1/0.824 * dat_hip_D$sedentary_mean_hip
```

### Figure S13: Agreement ICCs (DOMINANT)

```{r}
thigh_icc_df <- map_dfr(pa_rows, function(pheno) {
  icc_swl <- calculate_icc(
    df   = dat_thigh_D,
    col1 = paste0(pheno, "_mean_wrist"),
    col2 = paste0(pheno, "_mean_thigh"),
    fmt_sep = ","
  )

  tibble(
    phenotype = pheno,
    est = icc_swl$icc_est,
    lci = icc_swl$icc_lci,
    uci = icc_swl$icc_uci
  )
})

hip_icc_df <- map_dfr(pa_rows, function(pheno) {
  icc_raine <- calculate_icc(
    df   = dat_hip_D,
    col1 = paste0(pheno, "_mean_wrist"),
    col2 = paste0(pheno, "_mean_hip"),
    fmt_sep = ","
  )

  tibble(
    phenotype = pheno,
    est = icc_raine$icc_est,
    lci = icc_raine$icc_lci,
    uci = icc_raine$icc_uci
  )
})

vlines <- list(
  ggplot2::geom_vline(xintercept = 0.75,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4)

)

forestplot_labels <- data.frame(
  phenotype = pa_rows,
  label = unname(unlist(pa_labels[pa_rows]))
)

figure <- ckbplotr::forest_plot(
  list ("CAP-24 study (wrist vs. thigh)" = thigh_icc_df, "CAP-24 study (wrist vs. hip)" = hip_icc_df),
  row.labels = forestplot_labels,
  col.key = "phenotype",
  col.estimate = "est",
  col.lci = "lci",
  col.uci = "uci",
  exponentiate = FALSE,
  xlim = c(0, 1),
  xticks = c(0, 0.25, 0.5, 0.75, 1),
  xlab = c("ICC"),
  right.heading = "ICC (95% CI)",
  panel.width = unit(50, "mm"),
  base_size = 10,
  add = list(start = vlines)
)

ggsave(
  filename = here("output", "prepared", "figures", "Figure_S13.png"),
  plot = figure$plot,
  width = 23,
  height = 8,
  units = "cm",
  dpi = 300,
  bg = "white"
)
```

### Figure S14: Bland-Altman plots (DOMINANT)

```{r}
# Initialise constants
inner_pad <- 0.02   # fraction of npc to expand box
gap       <- 0.04   # relative gap between panels A and B

# Prepare individual scatter plots for SWL
plot1 <- make_bland_altman_plot(dat_thigh_D, 
                                'overall_activity_mean', 
                                'Overall activity',
                                phenotype_units = 'mg/day')

plot2 <- make_bland_altman_plot(dat_thigh_D, 
                                'steps_mean', 
                                'Step count',
                                phenotype_units = 'steps/day',
                                digits = 0)

plot3 <- make_bland_altman_plot(dat_thigh_D, 
                                'cadence_peak1_mean', 
                                'Peak 1-min cadence',
                                phenotype_units = 'steps/minute')

plot4 <- make_bland_altman_plot(dat_thigh_D, 
                                'mvpa_mean', 
                                'MVPA',
                                phenotype_units = 'minutes/day')

plot5 <- make_bland_altman_plot(dat_thigh_D, 
                                'lipa_mean', 
                                'Light physical activity',
                                phenotype_units = 'hours/day')

plot6 <- make_bland_altman_plot(dat_thigh_D, 
                                'sedentary_mean', 
                                'Sedentary behaviour',
                                phenotype_units = 'hours/day')

# Combine all SWL plots
panel_a <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)

# Prepare individual scatter plots for Raine
plot1 <- make_bland_altman_plot(dat_hip_D, 
                                'overall_activity_mean', 
                                'Overall activity',
                                phenotype_units = 'mg/day')

plot2 <- make_bland_altman_plot(dat_hip_D, 
                                'steps_mean', 
                                'Step count',
                                phenotype_units = 'steps/day',
                                digits = 0)

plot3 <- make_bland_altman_plot(dat_hip_D, 
                                'cadence_peak1_mean', 
                                'Peak 1-min cadence',
                                phenotype_units = 'steps/minute')

plot4 <- make_bland_altman_plot(dat_hip_D, 
                                'mvpa_mean', 
                                'MVPA',
                                phenotype_units = 'minutes/day')

plot5 <- make_bland_altman_plot(dat_hip_D, 
                                'lipa_mean', 
                                'Light physical activity',
                                phenotype_units = 'hours/day')

plot6 <- make_bland_altman_plot(dat_hip_D, 
                                'sedentary_mean', 
                                'Sedentary behaviour',
                                phenotype_units = 'hours/day')

# Combine all Raine plots
panel_b <- arrangeGrob(ggplotGrob(plot1),
                       ggplotGrob(plot2),
                       ggplotGrob(plot3),
                       ggplotGrob(plot4),
                       ggplotGrob(plot5),
                       ggplotGrob(plot6),
                       ncol = 3)


# Add titles to each panel
panel_a <- gridExtra::arrangeGrob(
  panel_a,
  top = grid::textGrob(
    "A. CAP-24 study (wrist vs. thigh)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

panel_b <- gridExtra::arrangeGrob(
  panel_b,
  top = grid::textGrob(
    "B. CAP-24 study (wrist vs. hip)",
    x = 0.02,
    y = 0.98,
    just = c("left", "top"),
    gp = grid::gpar(fontsize = 14, fontface = "bold")
  )
)

# Add black borders around each panel
panel_a <- grid::grobTree(
  panel_a,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"), 
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

panel_b <- grid::grobTree(
  panel_b,
  grid::rectGrob(
    x = 0.5, 
    y = 0.5,
    width  = unit(1, "npc") + unit(inner_pad, "npc"),
    height = unit(1, "npc") + unit(inner_pad, "npc"),
    gp = grid::gpar(fill = NA, col = "black", lwd = 1)
  )
)

# Stack the two boxed panels
figure <- gridExtra::arrangeGrob(panel_a,
                                 grid::nullGrob(),
                                 panel_b,
                                 ncol = 1,
                                 heights = c(1, gap, 1))

# Add small outer margin
figure <- ggplot() +
  theme_void() +
  annotation_custom(figure) +
  theme(plot.margin = grid::unit(c(0.5, 0.5, 0.5, 0.5), "cm"))

# Save figure to file
ggsave(filename = here("output", "prepared", "figures", "Figure_S14.png"),
       plot = figure,
       width = 21,
       height = 29.7,
       units = "cm",
       dpi = 300,
       bg = "white")
```

### Figure S15: Equivalence tests (DOMINANT)

```{r}
eq_zone <- 0.1

equi_test_swl_list <- list()
equi_test_raine_list <- list()

for (pheno in pa_rows) {

  res_swl <- equivalence_test(dat_thigh_D, paste0(pheno, "_mean"), eq_zone)
  res_raine <- equivalence_test(dat_hip_D, paste0(pheno, "_mean"), eq_zone)

  equi_test_swl_list[[pheno]] <- data.frame(
    phenotype = pheno,
    mean_ratio = res_swl$mean_ratio,
    lci = res_swl$lci,
    uci = res_swl$uci,
    is_equivalent = res_swl$is_equivalent
  )

  equi_test_raine_list[[pheno]] <- data.frame(
    phenotype = pheno,
    mean_ratio = res_raine$mean_ratio,
    lci = res_raine$lci,
    uci = res_raine$uci,
    is_equivalent = res_raine$is_equivalent
  )
}

equi_test_swl <- do.call(rbind, equi_test_swl_list)
equi_test_raine <- do.call(rbind, equi_test_raine_list)

row.names(equi_test_swl) <- NULL
row.names(equi_test_raine) <- NULL

vlines <- list(
  ggplot2::geom_vline(xintercept = 1 - eq_zone,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4),
  ggplot2::geom_vline(xintercept = 1 + eq_zone,
                      linetype = "dashed",
                      colour = "black",
                      linewidth = 0.4)
)

forestplot_labels <- data.frame(
  phenotype = pa_rows,
  label = unname(unlist(pa_labels[pa_rows]))
)

figure <- ckbplotr::forest_plot(
  list ("CAP-24 study (wrist vs. thigh)" = equi_test_swl, "CAP-24 study (wrist vs. hip)" = equi_test_raine),
  row.labels = forestplot_labels,
  col.key = "phenotype",
  col.estimate = "mean_ratio",
  col.lci = "lci",
  col.uci = "uci",
  exponentiate = FALSE,
  xlim = c(0.80, 1.20),
  xlab = c("Mean ratio (Thigh/Wrist)", "Mean ratio (Hip/Wrist)"),
  right.heading = "Mean ratio (90% CI)",
  nullval = TRUE,
  panel.width = unit(50, "mm"),
  base_size = 10,
  left.gap = c("I", "I"),
  add = list(start = vlines)
)

ggsave(
  filename = here("output", "prepared", "figures", "Figure_S15.png"),
  plot = figure$plot,
  width = 23,
  height = 8,
  units = "cm",
  dpi = 300,
  bg = "white"
)
```